Memory-aware Adaptive Scheduling of Scientific Workflows On Heterogeneous Architectures\\

### 2024-10-11 main.tex
temp - shall we discuss briefly for dynamic expe?

    \paragraph{Tiny cluster}
    The makespan in case of no recomputation becomes invalid as soon as at least one task finds itself in an invalid memory size
    situation - that is, if the scheduler assumed its memory to be smaller than it actually was and assigned it to a processor
    with not enough memory capacity.
    Due to an extremely constrained memory in the tiny cluster, only 134 experiments out of 1160 for all algorithm variants
    ended with a valid makespan withjout recomputation. $13$ experiments ended with a valid makespan after recomputation in case of \heft,
   $16$ in case of \heftmm, $50$ in case of \heftblc and $55$ in case of \heftbl.
    Figure~\ref{fig:updates-ms} shows the increase in makespan in case of no recomputation for these experiments.
    There were valid final makespans with no recomputation only for the smallest workflows - $56$ original ones, $47$ 200-task ones,
    $25$ 1000-task ones and $6$ 2000-task ones.

@@

    To be able to answer the runtime system without holding it up for too long, the scheduler needs to provide a fast answer.
    Our bottom-level-based heuristics \heftbl and \heftblc provide smaller running times and also scale better with growing workflow
    sizes~(see Fig.~\ref{fig:runtimes-abs} and Fig.~\ref{fig:runtimes-abs}).
    Their running times are similar and grow from tens of miliseconds for the smallest workflows to $25-27$ seconds for the largest workflows.
    \heftmm, however, needs to compute a memory-optimal traversal of the entire workflow to compute the ranks of the tasks,
    so its runnning time scales from also rens of miliseconds for the smalest workflows to thousands of seconds - $1172.7$ for \numprint{20000}-task workflows and
    $2994.9$ seconds for the largest, \numprint{30000}-task workflows.
    This increased running time is, though, offset by the unique $100\%$ success rate this algorithm shows when scheduling large
    workflows in difficult (memory-constrained) setups.

    \begin{figure}[tb]
        \centering
        \includegraphics[width=1.1\columnwidth] {images/runtimes-logarithmic}
        \caption{Running times of the heuristics and the baseline. The y axis ist logarithmic.}
        \label{fig:runtimes-log}
        \vspace{-0.3cm}
    \end{figure}

@@

\section{Conclusion  \skug{Full: 0, Polished: 0}}
\label{sec:conc}

>>>>

\AB{Any info on success rate of adaptive heuristic compared to static ones? 
For which cluster do we have some results? }

    \paragraph{Tiny cluster}
    The makespan in case of no recomputation becomes invalid as soon as at least one task finds itself in an invalid memory size
    situation - that is, if the scheduler assumed its memory to be smaller than it actually was and assigned it to a processor
    with not enough memory capacity.
    Due to an extremely constrained memory in the tiny cluster, only 134 experiments out of 1160 for all algorithm variants
    ended with a valid makespan without recomputation. $13$ experiments ended with a valid makespan after recomputation in case of \heft,
   $16$ in case of \heftmm, $50$ in case of \heftblc and $55$ in case of \heftbl.
    Figure~\ref{fig:updates-ms} shows the increase in makespan in case of no recomputation for these experiments.
    There were valid final makespans with no recomputation only for the smallest workflows - $56$ original ones, $47$ 200-task ones,
    $25$ 1000-task ones and $6$ 2000-task ones.

@@

    To be able to answer the runtime system without holding it up for too long, the scheduler needs to 
    be able to compute a schedule rapidly. %provide a fast answer.
    The bottom-level-based heuristics \heftbl and \heftblc provide smaller running times than \heftmm, 
    and also scale better with growing workflow
    sizes~(see Fig.~\ref{fig:runtimes-log}).
    Their running times are similar and grow from tens of milliseconds for the smallest workflows to $25-27$ seconds 
    for the largest workflows.
    \heftmm, however, needs to compute a memory-optimal traversal of the entire workflow to compute the ranks 
    of the tasks,
    so its running time scales from also tens of milliseconds for the smallest workflows, 
    to thousands of seconds - $1172.7$ for \numprint{20000}-task workflows and
    $2994.9$ seconds for the largest, \numprint{30000}-task workflows.
    This increased running time is, though, offset by the unique $100\%$ success rate this algorithm 
    obtained when scheduling large
    workflows in difficult (memory-constrained) setups.

    \begin{figure}[tb]
        \centering
        \includegraphics[width=1.1\columnwidth] {images/runtimes-logarithmic}
        \caption{Running times of the heuristics. The y axis is logarithmic.}
        \label{fig:runtimes-log}
        \vspace{-0.3cm}
    \end{figure}

@@

\section{Conclusion} %  \skug{Full: 0, Polished: 0}}
\label{sec:conc}
